---
title: "Dissertation Code"
author: "210155383"
date: "`r Sys.Date()`"
output: html_document
---

```{r packages}


library(tidyverse)
library(ggplot2)
library(magrittr)
library(car)
library(readxl)
library(rstatix)



```


IMPORT DF


```{r}


BetaDF <- read_excel("Both_Betas_WI.xlsx")

BetaDF %>% group_by(ROI, Hemisphere, Condition, Position) %>%
           subset(Hemisphere %in% c('Left', 'Right'))
           

BetaDF$Hemisphere <- factor(BetaDF$Hemisphere, levels = c("Combined", "Left", "Right"))
BetaDF$Position <- factor(BetaDF$Position, levels = c("1", "2", "3"))
BetaDF$Condition <- factor(BetaDF$Condition, levels = c("Same", "Diff", "Half"))
BetaDF$ROI <- factor(BetaDF$ROI, levels = c("OFA", "FFA"))

```


SUMMARY DATAFRAME


``` {r}

SummaryDF <- BetaDF %>%
  group_by(ROI, Hemisphere, Condition, Position) %>%
  summarise( 
    n=n(),
    mean=mean(Beta),
    sd=sd(Beta)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))




```


FOUR WAY ANOVA


```{r}


ANOVAdf <- subset(BetaDF, Hemisphere %in% c('Left', 'Right'))

get_anova_table(anova_test(data = ANOVAdf, dv = Beta, wid = Sample, within = c(Hemisphere, ROI, Condition, Position), effect.size = "pes"))


```


OFA BETA PLOT


```{r}


OFABetaSum <- SummaryDF %>%
              subset(ROI == "OFA") %>%
              subset(Hemisphere %in% c('Left', 'Right'))


ggplot(OFABetaSum, aes(x=Position, y=mean, fill = Condition)) +
      geom_bar(fun = "mean", stat = "summary") +
      geom_errorbar(aes(ymin=mean-se, ymax=mean+se, width = .1)) +
      scale_fill_manual("Condition", values = c("Same" = "steelblue4", "Diff" = "hotpink3", "Half" = "cyan4")) +
      facet_grid(Condition ~ Hemisphere, scales="free", space="free_x") +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,9), breaks = seq(2, 8, 2)) +
  ggtitle("OFA") +
  ylab("Beta Value") +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color="grey95"),
    panel.grid.minor = element_line(color="grey95"),
    strip.background=element_blank(),
    strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y=element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    panel.border = element_rect(size= .75,fill = NA,color = "black"))


# ggsave("OFA Plot", width = 7, height = 5.5)


```


FFA BETA PLOT


```{r}


FFABetaSum <- SummaryDF %>%
              subset(ROI == "FFA") %>%
              subset(Hemisphere %in% c('Left', 'Right'))


ggplot(FFABetaSum, aes(x=Position, y=mean, fill = Condition)) +
      geom_bar(fun = "mean", stat = "summary") +
      geom_errorbar(aes(ymin=mean-se, ymax=mean+se, width = .1)) +
            scale_fill_manual("Condition", values = c("Same" = "steelblue4", "Diff" = "hotpink3", "Half" = "cyan4")) +
      facet_grid(Condition ~ Hemisphere, scales="free", space="free_x") +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,9), breaks = seq(2, 8, 2)) +
  ggtitle("FFA") +
  ylab("Beta Value") +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color="grey95"),
    panel.grid.minor = element_line(color="grey95"),
    strip.background=element_blank(),
    strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y=element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    panel.border = element_rect(size= .75,fill = NA,color = "black"))


# ggsave("FFA Plot.jpeg", width = 7, height = 5.5)


```

LEFT FFA BETAS BY CONDITION


```{r}

lFFABetaSum <- FFABetaSum %>%
               subset(Hemisphere == "Left")



ggplot(lFFABetaSum, aes(x=Position, y=mean, fill = Condition)) +
      geom_bar(fun = "mean", stat = "summary") +
      geom_errorbar(aes(ymin=mean-se, ymax=mean+se, width = .1)) +
            scale_fill_manual("Condition", values = c("Same" = "steelblue4", "Diff" = "hotpink3", "Half" = "cyan4")) +
      facet_grid( . ~ Condition, scales="free", space="free_x") +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,9), breaks = seq(2, 8, 2)) +
  ggtitle("Left FFA") +
  ylab("Beta Value") +
  theme(#legend.position=c(.60,.85),
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color="grey95"),
    panel.grid.minor = element_line(color="grey95"),
    strip.background=element_blank(),
    strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y=element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    panel.border = element_rect(size= .75,fill = NA,color = "black"))


# ggsave("Figures/lFFA Plot.jpeg", width = 7, height = 3)



```


RIGHT FFA BETAS BY CONDITION


```{r}

rFFABetaSum <- FFABetaSum %>%
               subset(Hemisphere == "Right")


ggplot(rFFABetaSum, aes(x=Position, y=mean, fill = Condition)) +
      geom_bar(fun = "mean", stat = "summary") +
      geom_errorbar(aes(ymin=mean-se, ymax=mean+se, width = .1)) +
            scale_fill_manual("Condition", values = c("Same" = "steelblue4", "Diff" = "hotpink3", "Half" = "cyan4")) +
      facet_grid( . ~ Condition, scales="free", space="free_x") +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,9), breaks = seq(2, 8, 2)) +
  ggtitle("Right FFA") +
  ylab("Beta Value") +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color="grey95"),
    panel.grid.minor = element_line(color="grey95"),
    strip.background=element_blank(),
    strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y=element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    panel.border = element_rect(size= .75,fill = NA,color = "black"))


# ggsave("rFFA Plot.jpeg", width = 7, height = 3)

```


LEFT OFA BETAS BY CONDITION


```{r}

lOFABetaSum <- OFABetaSum %>%
               subset(Hemisphere == "Left")


ggplot(lOFABetaSum, aes(x=Position, y=mean, fill = Condition)) +
      geom_bar(fun = "mean", stat = "summary") +
      geom_errorbar(aes(ymin=mean-se, ymax=mean+se, width = .1)) +
            scale_fill_manual("Condition", values = c("Same" = "steelblue4", "Diff" = "hotpink3", "Half" = "cyan4")) +
      facet_grid( . ~ Condition, scales="free", space="free_x") +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,9), breaks = seq(2, 8, 2)) +
  ggtitle("Left OFA") +
  ylab("Beta Value") +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color="grey95"),
    panel.grid.minor = element_line(color="grey95"),
    strip.background=element_blank(),
    strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y=element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    panel.border = element_rect(size= .75,fill = NA,color = "black"))


# ggsave("lOFA Plot.jpeg", width = 7, height = 3)

```

 
RIGHT OFA BETAS BY CONDITION


```{r}

rOFABetaSum <- OFABetaSum %>%
               subset(Hemisphere == "Right")


ggplot(rOFABetaSum, aes(x=Position, y=mean, fill = Condition)) +
      geom_bar(fun = "mean", stat = "summary") +
      geom_errorbar(aes(ymin=mean-se, ymax=mean+se, width = .1)) +
            scale_fill_manual("Condition", values = c("Same" = "steelblue4", "Diff" = "hotpink3", "Half" = "cyan4")) +
      facet_grid( . ~ Condition, scales="free", space="free_x") +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,9), breaks = seq(2, 8, 2)) +
  ggtitle("Right OFA") +
  ylab("Beta Value") +
  theme(legend.position = "none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color="grey95"),
    panel.grid.minor = element_line(color="grey95"),
    strip.background=element_blank(),
    strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y=element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    panel.border = element_rect(size= .75,fill = NA,color = "black"))


# ggsave("rOFA Plot.jpeg", width = 7, height = 3)


```


STATISTICS REPLICATION (HEMISPHERE == "Combined")


``` {r}

## COMBINED FFA SAME

cFFA_same <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Combined") %>%
             subset(Condition == "Same") 

get_anova_table(anova_test(data = cFFA_same, dv = Beta, wid = Sample, within = Position)) # SUCCESS!!
pwc_cFFAs <- cFFA_same %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## FFA DIFF

cFFA_diff <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Combined") %>%
             subset(Condition == "Diff") 

get_anova_table(anova_test(data = cFFA_diff, dv = Beta, wid = Sample, within = Position))
pwc_cFFAd <- cFFA_diff %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## COMBINED FFA HALF

cFFA_half <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Combined") %>%
             subset(Condition == "Half") 

get_anova_table(anova_test(data = cFFA_half, dv = Beta, wid = Sample, within = Position))
pwc_cFFAh <- cFFA_half %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")

## COMBINED OFA SAME

cOFA_same <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Combined") %>%
             subset(Condition == "Same") 

get_anova_table(anova_test(data = cOFA_same, dv = Beta, wid = Sample, within = Position))
pwc_cOFAs <- cOFA_same %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")

## COMBINED OFA DIFFERENT

cOFA_diff <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Combined") %>%
             subset(Condition == "Diff") 

get_anova_table(anova_test(data = cOFA_diff, dv = Beta, wid = Sample, within = Position))
pwc_cOFAd <- cOFA_diff %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## COMBINED OFA HALF

cOFA_half <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Combined") %>%
             subset(Condition == "Half") 

get_anova_table(anova_test(data = cOFA_half, dv = Beta, wid = Sample, within = Position))
pwc_cOFAh <- cOFA_half %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


```


STATISTICS LEFT HEMISPHERE (HEMISPHERE == "Left")


```{r}

## LEFT FFA SAME

lFFA_same <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Left") %>%
             subset(Condition == "Same") 

get_anova_table(anova_test(data = lFFA_same, dv = Beta, wid = Sample, within = Position))
pwc_lFFAs <- lFFA_same %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")



## LEFT FFA DIFF

lFFA_diff <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Left") %>%
             subset(Condition == "Diff") 

get_anova_table(anova_test(data = lFFA_diff, dv = Beta, wid = Sample, within = Position))
pwc_lFFAd <- lFFA_diff %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## LEFT FFA HALF

lFFA_half <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Left") %>%
             subset(Condition == "Half") 

get_anova_table(anova_test(data = lFFA_half, dv = Beta, wid = Sample, within = Position))
pwc_lFFAh <- lFFA_half %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")

pwc_lFFAh


## LEFT OFA SAME

lOFA_same <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Left") %>%
             subset(Condition == "Same") 

get_anova_table(anova_test(data = lOFA_same, dv = Beta, wid = Sample, within = Position))
pwc_lOFAs <- lOFA_same %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## LEFT OFA DIFFERENT

lOFA_diff <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Left") %>%
             subset(Condition == "Diff") 

get_anova_table(anova_test(data = lOFA_diff, dv = Beta, wid = Sample, within = Position))
pwc_lOFAd <- lOFA_diff %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## LEFT OFA HALF

lOFA_half <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Left") %>%
             subset(Condition == "Half") 

get_anova_table(anova_test(data = lOFA_half, dv = Beta, wid = Sample, within = Position))
pwc_lOFAh <- lOFA_half %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


```


STATISTICS RIGHT HEMISPHERE (HEMISPHERE == "Right")


```{r}

## RIGHT FFA SAME

rFFA_same <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Right") %>%
             subset(Condition == "Same") 

get_anova_table(anova_test(data = rFFA_same, dv = Beta, wid = Sample, within = Position))
pwc_rFFAs <- rFFA_same %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## RIGHT FFA DIFF

rFFA_diff <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Right") %>%
             subset(Condition == "Diff") 

get_anova_table(anova_test(data = rFFA_diff, dv = Beta, wid = Sample, within = Position))
pwc_rFFAd <- rFFA_diff %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## RIGHT FFA HALF

rFFA_half <- BetaDF %>%
             subset(ROI == "FFA") %>%
             subset(Hemisphere == "Right") %>%
             subset(Condition == "Half") 

get_anova_table(anova_test(data = rFFA_half, dv = Beta, wid = Sample, within = Position))
pwc_rFFAh <- rFFA_half %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## RIGHT OFA SAME

rOFA_same <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Right") %>%
             subset(Condition == "Same") 

get_anova_table(anova_test(data = rOFA_same, dv = Beta, wid = Sample, within = Position))
pwc_rOFAs <- rOFA_same %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")

## RIGHT OFA DIFFERENT

rOFA_diff <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Right") %>%
             subset(Condition == "Diff") 

get_anova_table(anova_test(data = rOFA_diff, dv = Beta, wid = Sample, within = Position))
pwc_rOFAd <- rOFA_diff %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")


## RIGHT OFA HALF

rOFA_half <- BetaDF %>%
             subset(ROI == "OFA") %>%
             subset(Hemisphere == "Right") %>%
             subset(Condition == "Half") 

get_anova_table(anova_test(data = rOFA_half, dv = Beta, wid = Sample, within = Position))
pwc_rOFAh <- rOFA_half %>% pairwise_t_test(Beta ~ Position, paired = TRUE,p.adjust.method = "bonferroni")



```


LATERALISATION BY REGION HEMISPHERE COMPARISONS


``` {r}

# FFA LATERALISATION

FFA_df <- BetaDF %>%
          subset(ROI == "FFA") %>%
          subset(Hemisphere %in% c('Left', 'Right'))

get_anova_table(anova_test(data = FFA_df, dv = Beta, wid = Sample, within = c(Hemisphere, Condition, Position)))


# OFA LATERALISATION


OFA_df <- BetaDF %>%
          subset(ROI == "OFA") %>%
          subset(Hemisphere %in% c('Left', 'Right'))

get_anova_table(anova_test(data = OFA_df, dv = Beta, wid = Sample, within = c(Hemisphere, Condition, Position), effect.size = "pes"))

